The Aquarius Stream Progenitor Was Not A Globular Cluster: \\ Its History Could Be Far More Interesting\altaffilmark{1}

### 2012-12-20 2012-aqs/draft-aqs.tex
Added photometric temperature discussion + table

\shorttitle{AQS on MIKE}
\shortauthors{Casey et al}

@@

\title{The Aquarius Stream Progenitor Was Not A Globular Cluster: \\ Its History is Far More Interesting}

\author{Andrew R. Casey\altaffilmark{1,2} and distinguished collaborators}
\altaffiltext{1}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia}
\altaffiltext{2}{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research,
77 Massachusetts Avenue, Cambridge, MA 02139, USA}

@@

Stellar streams in the halo are relics from relatively recent minor mergers in the Milky Way. The positions and kinematics of stars within these streams are sensitive to the galactic potential. As such, they can collectively constrain the fraction and distribution of accreted matter in the stellar halo, the sub-halo mass function, as well as the shape and extent of dark matter in the Milky Way. Moreover, individual elemental abundances for stars within these streams reveal the chemodynamical evolution of the Galaxy.

Wide-field surveys have proved excellent sources for finding stellar streams. Dozens of streams reaching out up to 150\,kpc in the stellar halo have been identified through photometric selections and matched-filtering techniques. However, as \citet{Helmi;White_1999} point out, these methods are only successful for identifying substructures that are sufficiently distant from the solar neighbourhood. A nearby stream within $\sim{}$10\,kpc will not appear as an on-sky over-density. Such substructures would only be detectable by utilising both position and kinematic information.

% Talk about RAVE
It is therefore necessary to survey the kinematics of solar neighbourhood stars in order to detect nearby streams. The RAVE (Radial Velocity Experiment) began such a survey in 2003 and has observed spectra from over 500,000 stars across 17,000 deg$^{2}$. RAVE candidates were photometrically selected based only on their apparent magnitude of 9 $<$ I $<$ 13, and are therefore kinematically unbiased. The RAVE data releases have provided radial velocities \citep{steinmetz;et-al_2006} and estimates of stellar parameters \citep{zwitter;et-al_2008, siebert;et-al_2011} now for a subset of these observations.

% Identification of the aquarius stream
Using this data, \citet{williams;et-al_2011} identified a co-moving group of nearby ($0.5 \lesssim d \lesssim 10$\,kpc) stars in the direction of the Aquarius constellation. The artefact is most apparent when examining kinematics against galactic latitude for stars within $-70\,^\circ < b < -50\,^\circ$. \citet{williams;et-al_2011} employed a selection criteria of $-250 < V_{hel} < -150$\,km s$^{-1}$, $30\,^\circ < l < 75\,^\circ, J > 10.3$ and identified 15 stream candidates. The average heliocentric radial velocity of these members was found to be $V_{HELIO} = -199$\,km s$^{-1}$, with a dispersion of 27\,km s$^{-1}$. When compared to other streams identified in the halo, this is an unusually wide kinematic dispersion. Streams are generally considered to be kinematically cold, with dispersions of $\sigma_v < 8$\,km s$^{-1}$. The radial velocities outputted by the RAVE survey are described to be $\sim2$\,km s$^{-1}$, so the wide kinematic distribution appears to be real.

% is it a real substructure
\citet{williams;et-al_2011} quantified the statistical significance of the Aquarius substructure with comparisons to the Besancon and Galaxia models. After populating the models, the galaxy representations were discretized in $\Delta{}V_{hel}$ and $\Delta{}l$ grid blocks.

There is no reason to suspect that the Aquarius stream is not a real substructure.

% What is it?
Given the extent of stellar debris the Sagittarius dwarf has littered in the Milky Way, it is reasonable to suspect the Aquarius stream might be Sagittarius in origin. Although the metallicities reported by \citet{williams;et-al_2011} are not dissimilar from the stream, the distances and $V_{Z}$, $V_\phi$ for Aquarius are quite distinct from Sagittarius. \citet{williams;et-al_2011} concluded that the newly discovered stream could not be positively associated with the Monoceros stream, Hercules-Aquila cloud, or either the Canis Major or Virgo Overdensities.

% MRS follow-up by de boer
In order to investigate the Aquarius progenitor and any possible association with existing substructures, \citet{wylie-de-boer;et-al_2012} observed six Aquarius stream members with medium resolution (R = 25,000) spectroscopy. Their data indicates the stream is chemically coherant, with a dispersion in [Fe/H] of only 0.1\,dex. This minimal chemical scatter suggests that the Aquarius stream progenitor is a globular cluster, since dwarf spheroidal galaxies  exhibit chemical dispersions of a dex or more \citet{Frebel_Norris_2011}.

 Based on sodium and nickel abundance ratios with respect to iron, they claim the Aquarius stream chemical signatures unambiguously represent those of a globular cluster.

% globular cluster chemical signatures

We seek to investigate the globular cluster origin claim made by \citet{wylie-de-boer;et-al_2012}. We present a detailed chemical abundance analysis for five confirmed Aquarius stream members observed using the Magellan Inamori Kyocera Echelle spectrograph \citep{Bernstein;et-al_2003} on the Magellan telescope. Details of the observations and data reduction are outlined in the following section. The data analysis is presented in \S\ref{sec:analysis} and a detailed discussion of these results resides in \S\ref{sec:discussion}. In \S\ref{sec:conclusion} we present our conclusions and critical interpretations.

\section{Observations \& Data Reduction}

The most comprehensive sample of Aquarius stream stars is presented in the discovery paper of \citet{williams;et-al_2011}. Since the globular cluster origin claim of \citet{wylie-de-boer;et-al_2012} is based from a subset of six of these stars, we targeted stars largely from this study. Four of our stars are in common with \citet{wylie-de-boer;et-al_2012}. An additional star from the original \citet{williams;et-al_2011} sample, J2306265-085103, was also observed. J2306265-085103 had insufficient S/N for the RAVE pipeline to accurately determine stellar parameters, so its membership hinges on radial velocity measurements. Program stars were observed in July 2011 and we observed X standard stars observed for a separate program in March 2011. All observations were taken using the 1.0" slit, which provides a spectral resolution of $R = 28,000$. The exposure times for our program stars varied per star from X seconds to Y seconds to ensure a signal-to-noise in excess of 100 per pixel element at 600 nm for all stars.

The data were reduced using the CarPy pipeline. Standard flat-fielding and extraction methods were employed using 10 quartz and 10 milky frames taken at the start of each night. ThAr arc lamp exposures were taken at the start of each night to provide wavelength calibration. No telluric corrections were made as atmospheric absorption does not affect any of the transitions in our line list. Each reduced echelle order was carefully normalised using a third order spline. All normalised orders were stitched together to provide a single one-dimensional spectrum from 3800-9400\,\AA{}.

@@

\subsection{Radial Velocities}
\label{sec:radial-velocities}
The radial velocity for each star was determined in a two-step method. An initial estimate of the radial velocity was ascertained by cross-correlation with a synthetic spectrum of a giant with $T_{eff} = 4500$\,K, $\log{g} = 1.5$, and [M/H] $= -1.0$ across the wavelength range $8450 - 8700$ \AA{}. The spectrum was shifted to rest frame using this initial velocity. Velocities found from cross-correlation are typically within 1\,km\,s$^{-1}$ of our final published value.

With our spectrum at near-rest, we measured the equivalent widths of $N$ lines by fitting Gaussian functions to the absorption profiles. Fitting Gaussian profiles provides us with the measured equivalent width, the full-width half-maximum of the profile, and the central wavelength. Thus, the residual radial velocity can be found from the ratio of the central and rest line wavelengths. The final radial velocity for the star is provided by the mean of these $N$ line velocity measurements. Figure \ref{fig:line-velocities} shows the line velocities for HD41667 after  being placed at rest using our cross-correlation velocity of 314.4\,km s$^{-1}$. As expected, the mean offset is small ($-0.75$\,km s$^{-1}$), and our standard deviation is 0.79\,km s$^{-1}$ from 164 line measurements. This provides us with a final measured radial velocity of $313.7 \pm 0.1$\,km s$^{-1}$. This process was repeated for all observations. The radial velocities published in Table \ref{tab:observations} are the final values from this two-step method. Heliocentric velocities agree excellently (within X\,km s$^{-1}$) with previously reported literature values \citep{williams;et-al_2011,wylie-de-boer;et-al_2012}.

\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/line-velocity.pdf}
	\caption{Residual velocities for each absorption line with a well-fitted Gaussian profile after correcting for the doppler shift with our cross-correlation measurement. The mean residual velocity is within our uncertainties derived from cross-correlation.}
	\label{fig:line-velocities}
\end{figure}

@@

For the measurement of atomic absorption lines, we employed the line list of \citet{yong;et-al_2005} with additional transitions of Cr, Sc, Zn, and Sr from \citet{frebel;et-al_2010}. We supplemented the list with hyperfine-structure data for Sc and Mn from the Kurucz compilation \citet{Kurucz;1998}. Molecular line data for CH was taken from \citet{Plez;et-al_2008,Plez;et-al_2009}. For lines with hyperfine structure, blended transitions or molecular features, we determined the transition abundance using a spectral synthesis approach where the abundance of a given species is found by by matching a synthetic spectrum to the observed spectrum.

The equivalent widths for all transitions were measured automatically using software for this study. Given the rest wavelength and an initial guess of the FWHM, a Gaussian function is iteratively fitted to the absorption profile. At the same time, the local continuum is found within 20\,\AA{} either side of the rest wavelength using a second-order polynomial. Measuring the local continuum ensures any errors in our initial normalisation or order-stitching do not propagate through to our equivalent width measurements. Any group of pixels that deviate significantly ($>2\sigma$) to the local continuum are cosmic ray hits, or more likely trough points of a neighbouring profile. We attempt to fit a Gaussian profile to each of these groups of deviating pixels, using the best estimate of the local continuum. If a profile is successfully fitted, then all points belonging to that profile are excluded from the continuum determination. When fitting Gaussian profiles, the $\chi^2$ difference between the observation and the profile is minimized. In order to account for blended transitions, our $\chi^2$ function is weighted based on the distance to the rest wavelength. Pixels near the rest wavelength are weighted higher than those on the wings. Although this approach relies on a reasonably accurate ($<4$\,km s$^{-1}$) radial velocity correction, it greatly improves the accuracy of the equivalent width measurements.

We note that the results of our iterative fitting approach are entirely insensitive to the initial FWHM guess. Increasing the initial guess from 0.1\,\AA{} to 1 or 2\,\AA{} -- an unphysical large value for high-resolution spectra -- does not alter any of our equivalent width measurements. Only a small increase in computational cost is observed. Although we are confident in our automatic equivalent width measurements, every absorption profile was examined by eye for quality.

We list the atomic data and measured equivalent widths for atomic lines used during this analysis in Table \ref{tab:equivalent-widths}. Saturated lines were excluded by removing measurements with reduced equivalent widths, $\log_{10}{(EW/\lambda)} > -4.5$\, dex. A minimum detectable equivalent width was calculated as a function of wavelength based on the S/N, and only lines that exceeded a $3\sigma$ detection significance were included. We have verified our equivalent width measurement techniques by comparing our measurements for 164 lines in HD140283 with the study of \citet{Norris;et-al_1996}. Excellent agreement is found between the two studies, which is illustrated in Figure \ref{fig:ew-compare}. The mean difference between this study and that of \cite{norris;et-al_1996} is a negligible $0.64 \pm 2.78$\,m\AA{}, and no systematic trend is present.

% equivalent widths plot with Norris for HD 122563
\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/smh-norris.pdf}
	\caption{A comparison showing equivalent widths measured for HD140283 using an automatic routine (see \S\ref{sec:line-measurements}), and those found with careful hand measurements by \citet{norris;et-al_1996}. No systematic trend is present, and the mean difference between these studies is $\langle\Delta{}W_\lambda = -0.64 \pm 2.78$ m\AA{}.}
	\label{fig:ew-compare}
\end{figure}

@@

\subsection{Model Atmospheres}
We employed the ATLAS9 stellar atmospheres of \citet{Castelli;Kurucz_2003} for this analysis. These one-dimensional models ignore any centre-to-limb spatial variations, assume hydrostatic equilibrium and no convective overshoot from the photosphere. Absorption lines are assumed to form under the assumption of local thermal equilibrium. The stellar parameter spacing for these grid models is 250\,K, 0.5\,dex in surface gravity, 0.5\,dex in [M/H] and 0.1\,dex in [$\alpha$/Fe]. We interpolated the atmospheric densities, temperatures, electron pressures at all depths between stellar atmospheres using the Quickhull algorithm for this analysis. Quickhull is reliant on Delaunay tessellation, which suffers from extremely skewed cells when the grid points vary in size by orders of magnitude -- as $T_{eff}$ values do compared to $\log{g}$ or [X/H]. If unaccounted for, these asymmetric cells can manifest as significant errors in interpolated densities, temperatures, pressures, and opacities across all photospheric depths. We scaled each stellar parameter between zero and unity prior to interpolation to minimise these errors. During this step, $\log{g}$, [Fe/H] and [$\alpha$/Fe] points were scaled such that we simultaneously interpolate linearly in $T_{eff}$ and logarithmically in all other parameters.

\subsection{Stellar Parameters}
The most recent version of the spectral synthesis code MOOG \citep{Sneden;et-al_1973} has been used to derive individual line abundances and stellar parameters. This version employs a more accurate treatment of Rayleigh scattering \citep{Sobeck;et-al_2011}, which is particularly important for transitions blueward of 450\,nm. This is noteworthy, but is less relevant for this analysis as most of our line measurements are redward of 450\,nm. We have scaled our abundances to solar values using the chemical composition of \citet{Asplund;et-al_2009}.

\subsubsection{Photometric Effective Temperatures}

The effective temperatures published for all of our stars in Table \ref{sec:stellar-parameters} were derived spectroscopically (see \S\ref{sec:effective-teffs}). For consistency, we have also estimated effective temperatures using 2MASS infrared photometry. The $J-K$ colour has been employed for these calculations because it has the least dependence on metallicity. The Aquarius stream is relatively close and at high-latitude, so significant extinction by dust is note expected. Nevertheless, the dust maps of \citet{Schlegel;et-al_1998} have been used to estimate the effect of extinction along the line-of-sight. Two different $T_{eff}$-colour relationships have been used for estimating temperatures: the \citet{Alonso;et-al_1999} calibration for dwarfs/sub-giants, and the ? calibration for giants. All photometrically-derived temperatures are listed in \ref{tab:photometric-temperatures}.

@@

>>>>

\shorttitle{The Aquarius Stream Progenitor Was Not A Globular Cluster}
\shortauthors{Casey et al}

@@

\title{The Aquarius Stream Progenitor Was Not A Globular Cluster: \\ Its History Could Be Far More Interesting\altaffilmark{1}}

\author{Andrew R. Casey\altaffilmark{2,3} and distinguished collaborators}
\altaffiltext{1}{This paper includes data gathered with the 6.5 meter Magellan Telescopes located at Las Campanas Observa- tory, Chile.}
\altaffiltext{2}{Research School of Astronomy \& Astrophysics, Australian National University, Mount Stromlo Observatory, via Cotter Rd, Weston, ACT 2611, Australia; acasey@mso.anu.edu.au}
\altaffiltext{3}{Massachusetts Institute of Technology, Kavli Institute for Astrophysics and Space Research,
77 Massachusetts Avenue, Cambridge, MA 02139, USA}

@@

Stellar streams arise from tidal effects as satellite systems infall onto the Milky Way. The phase space information of stars within such streams are sensitive to the galactic potential. Therefore, they can collectively constrain the fraction and distribution of accreted matter in the stellar halo, the sub-halo mass function, as well as the shape and extent of dark matter in the Milky Way. Moreover, individual elemental abundances for stars within these streams help unravel the chemical evolution of the Galaxy. 
% Consider adding a final sentence about the amount of work that has gone into stellar streaams

Wide-field surveys have proved excellent sources for finding galactic substructures, including stellar streams. Dozens of streams reaching out up to 150\,kpc in the halo have been identified through photometric selections and matched-filtering techniques \citep{Belokurov;et-al_2007;Koposov_SG1}. However, as \citet{Helmi;White_1999} point out, these approaches are only successful for identifying substructures that are sufficiently distant from the solar neighbourhood. A nearby stream within $\sim{}$10\,kpc will not appear as an on-sky over-density, as the stars would be sparsely positioned across the sky. Such substructures would only be detectable with kinematic, or perhaps precise chemical information.

% Talk about RAVE
It is therefore necessary to survey solar neighbourhood stars with spectroscopy in order to detect any nearby substructures. The RAVE (Radial Velocity Experiment) began such a survey in 2003 and has observed spectra from over 500,000 stars across 17,000 deg$^{2}$. As the name suggests, the primary goal of RAVE was to obtain radial velocities for the solar neighbourhood and beyond. In an attempt to remain kinematically unbiased, RAVE candidates were selected based only on their apparent magnitude. With the exception of bulge stars where some photometric cuts were employed, all stars between 9 $<$ I $<$ 13 were observed. Almost all of these candidates have published radial velocity measurements \citep{steinmetz;et-al_2006}, and for a subset of stars with sufficient S/N, estimates of stellar parameters have been derived using a $\chi^2$ minimization technique \citep{zwitter;et-al_2008, siebert;et-al_2011}.

% Identification of the aquarius stream
Using these data, \citet{williams;et-al_2011} identified a co-moving group of nearby ($0.5 \lesssim d \lesssim 10$\,kpc) stars in the vicinity of the Aquarius constellation $(l, b) = (60\,^\circ, -55\,^\circ)$. The artefact is most apparent when examining kinematics against galactic latitude for stars within $-70\,^\circ < b < -50\,^\circ$. \citet{williams;et-al_2011} employed a selection criteria of $-250 < V_{HEL} < -150$\,km s$^{-1}$, $30\,^\circ < l < 75\,^\circ, J > 10.3$ to maximize the contrast between the stream and halo background, identifying 15 stream candidates in the process. The average heliocentric radial velocity of these members was found to be $V_{HEL} = -199$\,km s$^{-1}$, with a dispersion of 27\,km s$^{-1}$. The radial velocities outputted by the RAVE survey are described to be $\sim2$\,km s$^{-1}$, so the wide kinematic distribution appears to be real.

%When compared to other streams identified in the halo, this is an unusually wide kinematic dispersion. Streams are generally considered to be kinematically cold, with dispersions of $\sigma_v < 8$\,km s$^{-1}$.

% QUANTIFYING THE STREAM DETECTION
Upon examining the galactic longitude and radial velocities of Aquarius stars, the stream appears quite distinct from the halo. In order to quantify the statistical likelihood that the Aquarius stream is a true substructure, \citet{WIlliams;et-al_2011} compared the number of observed RAVE stars within $-70\,^\circ < b < -50\,^\circ$ against the Galaxia \citep{Sharma;et-al_2009} and Besan\c{c}on \citep{Robin;et-al_2003} galaxy models. Predicted particles and observed stars between $-70\,^\circ < b < -50\,^\circ$ were binned in $\Delta{l} \times \Delta{V_{hel}}$ using varying grid cell sizes between $25-70\,^\circ$ and 20-100\,km s$^{-1}$ respectively. The significance of the stream is calculated for each cell. \citet{williams;et-al_2011} found the stream to be statistically significant ($>$4-$\sigma$) in 96\% of the grid cell sizes employed for the Besan\c{c}on model. By sampling the Galaxia model multiple times with varying extinction models, a similar result was found: between $75\pm15$\,\% to $80\pm18$\,\% of grid cells showed the Aquarius stream to significant at the 4-$\sigma$ level. Given the high-latitude of the stream and proximity of the stream, it is not surprising that dust had a negligible effect on the overall significance. \citet{williams;et-al_2011} concluded that the over-density in $l, V_{hel}$ is a true substructure, and neither the choice of galaxy model, cell size, nor the extinction model made any real difference to the stream detection significance.

% STREAM IS LOCALIZED
% the stream appears to be quite localized in space.
% nearby streams could be strewn out over several degrees. the Orphan stream wraps over 60 degrees in the sky, and the Sgr stream wraps several steradians

% DISTANCE AND DYNAMICS
% heliocentric + galactic velocities suggest the aquarius stream stars are in the halo, and not associated with the disk.
% distances

Given the extent of stellar debris the Sagittarius dwarf has littered throughout the Milky Way, it is reasonable to suspect the Aquarius stream might originate from the Sagittarius dwarf. Indeed, the Aquarius stream stars do not lie far from the orbital plane of Sagittarius and the metallicities reported by \citet{williams;et-al_2011} are not dissimilar from the Sagittarius stream. However, \citet{williams;et-al_2011} found the Aquarius $XYZ$ positions and kinematics (specifically $V_{Z}$ and $V_\phi$) are quite distinct from Sagittarius. Based on the phase space information available, \citet{williams;et-al_2011} concluded that the newly discovered stream could not be positively associated with the Monoceros stream, Hercules-Aquila cloud, or either the Canis Major or Virgo over-densities.

The Aquarius stream has a metallicity of $\mbox{[Fe/H]} \sim -1.0$, slightly more metal-rich than halo stars at the same distance. The dispersion in the stream's metallicity has yet to be fully characterised. \citet{williams;et-al_2011} found the stream to have an average of $\mbox{[M/H]} = -1.0 \pm 0.4$, compared to $\mbox{[M/H]} = -1.1 \pm 0.6$ for background stars after the same selection cuts had been employed. Of the 12 Aquarius stars in the \citet{williams;et-al_2011} discovery sample with stellar parameters, the metallicity range is wide: between --2.02 and --0.33 dex. Spectroscopic observations of higher resolution and S/N are necessary to accurately determine the metallicity distribution function. To this end, \citet{wylie-de-boer;et-al_2012} obtained high-resolution ($R = 25,000$) spectra with modest S/N ($\sim$30 pixel$^{-1}$) for six Aquarius stream giants. Their data indicated a much narrower metallicity distribution: $\mbox{[Fe/H]} = -1.09 \pm 0.10$\,dex extending between $\mbox{[Fe/H]} = -1.25$ to $-0.98$\,dex; the level of negligible intrinsic chemical scatter which is typically observed in globular clusters. The largest [Fe/H] discrepancy between the two studies was $\Delta\mbox{[Fe/H]} = -0.66$\,dex for the most metal-rich star in the \citet{williams;et-al_2011} sample. The most metal-poor star in the \citet{williams;et-al_2011} study was not observed by \citet{wylie-de-boer;et-al_2012}.

%The chemical coherence in the \citet{wylie-de-boer;et-al_2012} study is most intriguing.

In addition to ascertaining stellar parameters, \citet{wylie-de-boer;et-al_2012} measured light element abundances for the Aquarius stream stars -- the only study to do so until now. Primarily they focussed on Na, O, Ni, Mg, and Al abundances. Chemical patterns in these light elements arise as natural consequences of nucleosynthetic processes in massive stars. Most notably, an anti-correlation in sodium and oxygen abundance has been identified in all well-studied globular clusters to date. Originally this was thought to arise from internal mixing along the giant branch. However, dwarf stars were found to exhibit strong Na-enhancement and O-depletions, contrary to what would be expected if the Na-O anti-correlation was purely a result of internal mixing. It is well known now that photospheric abundance variations resulting from internal mixing are limited to C, N and Li. The Na-O pattern provides the best evidence that stars have formed in a globular cluster environment and that their chemical enrichment history has been dominated by Sn II events. From high-resolution spectroscopy of five stars in Aquarius, four of which had Na, O measurements, \citet{wylie-de-boer;et-al_2012} found two stars with super-solar sodium; slightly higher [Na/Fe] ratios for halo stars of the same metallicity. No strong oxygen depletion was evident in their stars.

There are other abundances patterns that allow us to infer the chemical evolution of a given cluster. \citet{Nissen;Schuster_1997} first noted that only the distant solar neighbourhood stars were enriched in [Ni/Fe] and [Na/Fe]. \citet{fulbright;et-al_2000} came to a similar conclusion: only somewhat distant ($R_\odot > 20$\,kpc) stars are likely to be sodium deficient. If the stellar halo has been built up from the accretion of smaller dwarf satellites, \citet{Nissen;Schuster_1997} proposed that this chemical trend may be indicative of the halo merger history. Although there are some caveats to this chemical pattern (see \S\ref{sec:ni-na-relation}), at the very least the Na-Ni correlation may provide an indication whether stars became chemically enriched in dSph-like environments. \citet{wylie-de-boer;et-al_2012} found all their Aquarius stars to be enriched in both sodium and nickel; contrary to what would be expected if the stars originated from a disrupted dSph satellite.

Combined with the low level of chemical scatter present in their sample, these chemical indicators led \citet{wylie-de-boer;et-al_2012} to conclude that the Aquarius stream must be the result of a tidally disrupted globular cluster. \citet{williams;et-al_2011} had previously precluded this possibility after modelling an Aquarius-like progenitor infalling onto the Milky Way and comparing the predicted $l, b, V_{hel}$ with known, nearby globular clusters of similar metallicities. However, no known globular cluster could match their simulation.

We seek to investigate the nature of the Aquarius stream, in particular the recent globular cluster origin claim made by \citet{wylie-de-boer;et-al_2012}. We present a detailed analysis for five confirmed Aquarius stream members from high-resolution, high S/N observations taken using the Magellan Inamori Kyocera Echelle spectrograph \citep{Bernstein;et-al_2003} on the Magellan Clay telescope. Our analysis includes determining the galactic dynamics and orbital paths for the Aquarius stream, and measuring precise chemical abundances. Details of the observations and data reduction are outlined in the following section. The data analysis is chronicalled in \S\ref{sec:analysis} and a detailed discussion of these results resides in \S\ref{sec:discussion}. In \S\ref{sec:conclusion} we present our conclusions and critical interpretations.

\clearpage
\section{Observations \& Data Reduction}

The most comprehensive sample of Aquarius stream stars is presented in the discovery paper of \citet{williams;et-al_2011}. Our sample includes five stars: four common to the \citet{wylie-de-boer;et-al_2012} study, and an additional star from the original \citet{williams;et-al_2011} sample. The additional star, J2306265-085103, had insufficient S/N in the RAVE sample for stellar parameters to be accurately determined. Program stars were observed in July 2011 in good seeing at high airmass (Table \ref{tab:observations}), and X standard stars were observed as part of a separate program in March 2011. All observations were taken using the 1.0'' slit, providing a spectral resolution of $R = 28,000$. The exposure times for our program stars varied per star from X-Y seconds to ensure a Signal-to-Noise ratio (S/N) in excess of 100 per pixel element at 600 nm.

Calibration frames were taken at the start of each night, including twenty flat-field frames (10 quartz, 10 milky) and 10 Th-Ar arc lamp exposures for wavelength calibration. The data were reduced using the CarPy pipeline\footnote{carpy website url}. One of our standard stars, HD 41667, was also reduced using standard extraction and calibration methods in \textsc{IRAF}. The resultant spectra from both reduction workflows were compared for residual fringing, S/N, and wavelength calibration. No noteworthy differences were present, and the CarPy pipeline was utilized for the remainder of our reductions. Each reduced echelle order was carefully normalised using a third order spline. Normalised orders  for a given star were stitched together to provide a single one-dimensional spectrum from 3800-9400\,\AA{}.

The white dwarf HR 6141 was observed on X with a S/N of 400 pixel$^{-1}$ to account for telluric absorption. The S/N for HR 6141 exceeds the S/N in any of our program stars. Although the atmospheric conditions are certain to change throughout the night and between observing runs, we are primarily using this spectra to identify lines that are affected by telluric absorption. Critical transitions necessary for abundance analyses that are affected by the earth's atmosphere are later corrected for telluric absorption (see \S\ref{sec:telluric-absorption}), but great attention is paid to telluric band-heads at X and X such that we are not over- or under-correcting the atmospheric absorption.

@@

\subsection{Radial Velocities}
\label{sec:radial-velocities}
The radial velocity for each star was determined in a two-step method. An initial estimate of the radial velocity was ascertained by cross-correlation with the synthetic spectrum of a giant with $T_{eff} = 4500$\,K, $\log{g} = 1.5$, and [M/H] $= -1.0$ across the wavelength range $8450 - 8700$ \AA{}. The observed spectrum was shifted to the pseudo-rest frame using this initial velocity. Velocities found from cross-correlation are typically within 1\,km\,s$^{-1}$ of our final published value.

With our spectrum at near-rest, we measured the equivalent widths of $\sim$200 lines by fitting Gaussian functions to the absorption profiles. Fitted Gaussian profiles provides us with a measured equivalent width, the full-width half-maximum of the profile, and the central wavelength. Thus, the residual radial velocity can be found from the ratio of the central and rest line wavelengths. The final radial velocity for the star is provided by the mean of these $\sim$200 line velocity measurements. Figure \ref{fig:line-velocities} shows the line velocities for HD41667 after being placed at pseudo-rest using our cross-correlation velocity of 314.4\,km s$^{-1}$. As expected, the mean residual offset is small ($-0.75$\,km s$^{-1}$), and our standard deviation is 0.79\,km s$^{-1}$ from 164 line measurements. This provides us with a final measured radial velocity of $313.7 \pm 0.1$\,km s$^{-1}$. This process was performed for all observations. The radial velocities published in Table \ref{tab:observations} are the final values from this two-step method. Heliocentric velocities agree excellently (within X\,km s$^{-1}$) with previously reported literature values \citep{williams;et-al_2011,wylie-de-boer;et-al_2012}, demonstrating the accuracy of the radial velocities published by the RAVE survey.

\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/line-velocity.pdf}
	\caption{Residual velocities for each absorption line with a well-fitted Gaussian profile after correcting for  doppler shift with our initial cross-correlation measurement. The mean residual velocity $-0.75$\,km\,s$^{-1}$ is within the 1-$\sigma$ cross-correlation uncertainty of $\pm0.9$\,km\,s$^{-1}$.}
	\label{fig:line-velocities}
\end{figure}

@@

For the measurement of atomic absorption lines, we employed the line list of \citet{yong;et-al_2005} with additional transitions of Cr, Sc, Zn, and Sr from \citet{frebel;et-al_2010}. We supplemented the list with hyperfine-structure data for Sc and Mn from the Kurucz compilation \citet{Kurucz;1998}. Molecular line data for CH was taken from \citet{Plez;et-al_2008,Plez;et-al_2009}. For lines with hyperfine structure, blended transitions or molecular features, we determined the transition abundance using a spectral synthesis approach where the abundance of a given species is found by by matching a synthetic spectrum to the observed spectrum. Equivalent widths were measured to determine the abundances of all other transitions.

The equivalent widths for all absorption lines were measured automatically using software written for this study. Given the rest wavelength and an initial guess of the full-width half-maxium (FWHM), a Gaussian function is iteratively fitted to the absorption profile. At the same time, the local continuum is found within 20\,\AA{} either side of the rest wavelength using a second-order polynomial. Measuring the local continuum ensures any errors in our initial normalisation or order-stitching do not propagate through to our equivalent width measurements. Any group of pixels that deviate significantly ($>$2-$\sigma$) from the local continuum are either persistent cosmic ray hits, or trough points of a neighbouring absorption profile. We attempt to fit a Gaussian profile to each group of deviating pixels, using the current best estimate for the local continuum. If a Gaussian profile is successfully fitted to the deviating group and its surrounding pixels, then all points belonging to that profile are excluded from the continuum determination. When fitting Gaussian profiles, the $\chi^2$ difference between the observation and the profile is minimized. In order to account for crowded absorption regions where the $\chi^2$ value might be influenced by a nearby profile, our $\chi^2$ function is weighted based on the distance to the rest wavelength by the function

\begin{equation}
W_{\lambda_{i}} = 1 + \exp{\left(\frac{-(\lambda_{i} - \lambda_{r})^2}{4\sigma^2}\right)}
\label{eq:chi-weight}
\end{equation}

\noindent where $\lambda_{r}$ (rest wavelength) and $\sigma$ are free parameters during the iterative fitting process. As a consequence of Eq. \ref{eq:chi-weight}, pixels near the rest wavelength are weighted higher than those on the wings, forcing the fit to disregard blended or crowded regions. Although this approach relies on a reasonably accurate radial velocity correction ($<$4\,km s$^{-1}$; which is easily achieved), it greatly improves the accuracy of the equivalent width measurements.

We note that the results of our iterative fitting approach are \textit{completely insensitive} to the initial FWHM guess. Increasing the initial FWHM estimate from 0.1\,\AA{} to 1 or 2\,\AA{} -- unphysically large values for high-resolution spectra -- does not alter \textit{any} of our final equivalent width (or FWHM) measurements. Only a small increase in computational cost is observed. Although we are extremely confident in our automatic equivalent width measurements, every absorption profile was examined by eye for quality, and spurious measurements were excluded.

We list the atomic data and measured equivalent widths for atomic lines used during this analysis in Table \ref{tab:equivalent-widths}. Saturated lines were excluded by removing measurements with reduced equivalent widths, $\log_{10}{(EW/\lambda)} > -4.5$\, dex. A minimum detectable equivalent width was calculated as a function of wavelength based on the S/N, and only lines that exceeded a $3\sigma$ detection significance were included. We have verified our equivalent width measurement techniques by comparing our measurements for 164 lines in HD140283 with the study of \citet{norris;et-al_1996}. Excellent agreement is found between the two studies, which is illustrated in Figure \ref{fig:ew-compare}. The mean difference between this study and that of \cite{norris;et-al_1996} is a negligible $0.64 \pm 2.78$\,m\AA{}, and no systematic trend is present.

% need to mention that we only used the "Good" Norris measurements

% equivalent widths plot with Norris for HD 122563
\begin{figure}[h]
	\includegraphics[width=\columnwidth]{./figures/smh-norris.pdf}
	\caption{A comparison showing equivalent widths measured for HD140283 using our automatic routine (see \S\ref{sec:line-measurements}), and those found with careful hand measurements by \citet{norris;et-al_1996}. No systematic trend is present, and the mean difference between these studies is $\langle\Delta{}W_\lambda\rangle = -0.64 \pm 2.78$ m\AA{}.}
	\label{fig:ew-compare}
\end{figure}

@@

\subsection{Model Atmospheres}
The ATLAS9 plane-parallel stellar atmospheres of \citet{Castelli;Kurucz_2003} have been used to deduce stellar parameters and abundances for all of our stars. These one-dimensional models ignore any centre-to-limb spatial variations, assume hydrostatic equilibrium and no convective overshoot from the photosphere. The stellar parameter spacing for these grid models is 250\,K, 0.5\,dex in surface gravity, 0.5\,dex in [M/H] and 0.1\,dex in [$\alpha$/Fe]. We interpolated the atmospheric pressures, densities, temperatures, and opacities between stellar atmospheres using the Quickhull algorithm \citep{Barber;et-al_1996}. Quickhull is reliant on Delaunay tessellation, which suffers from extremely skewed cells when the grid points vary in size by orders of magnitude -- as $T_{\mbox{eff}}$ values do compared to $\log{g}$ or [X/H]. If unaccounted for, performing interpolation using these asymmetric cells can manifest as significant errors in atmospheric properties across all photospheric depths. We scaled each stellar parameter between zero and unity prior to interpolation in order to minimise these errors. During this step, $\log{g}$, [M/H] and [$\alpha$/Fe] points were scaled such that we simultaneously interpolate linearly in $T_{eff}$ and logarithmically in all other parameters.

\subsection{Stellar Parameters}
The most recent version of the spectral synthesis code MOOG \citep{Sneden;et-al_1973} has been used to derive individual line abundances and stellar parameters. This version of MOOG employs Rayleigh scattering \citep{Sobeck;et-al_2011} instead of treating scattering as true absorption, which is particularly important for transitions blue-ward of 450\,nm. This is noteworthy, but is less relevant for this analysis as most of our line measurements are red-ward of 450\,nm. Absorption lines are assumed to form under the assumption of local thermal equilibrium.

@@

\subsubsection{Photometric Effective Temperatures}
\label{sec:photometric-temperatures}

The effective temperatures published for all of our stars in Table \ref{sec:stellar-parameters} have been derived spectroscopically (see \S\ref{sec:effective-teffs}). As a consistency check for our spectroscopic temperatures, we have also estimated effective temperatures using infrared photometry from the 2MASS catalog. The $J-K$ colour has been employed for these calculations because it has the least dependence on metallicity.
